### 2021-01-16 priority-cp.tex
Minor rewrites; reformatted typing sugar in appendices.

\subsubsection*{Priorities}
The function $\pr(\cdot)$ returns smallest priority of a type. As with PGV, the type system guarantees that the top-most connective always holds the smallest priority.  The function $\minpr(\cdot)$ returns the \emph{minimum} priority of all types a typing context, or $\cs{\ptop}$ if the context is empty:
\[
  \usingnamespace{pcp}
  \setlength{\arraycolsep}{1pt}
  \begin{array}{lclclcl}
    \pr(\ty{\tyone[\cs{o}]})        & = & \cs{o} \\
    \pr(\ty{\tybot[\cs{o}]})        & = & \cs{o}
  \end{array}
  \qquad
  \begin{array}{lclclcl}
    \pr(\ty{\tytens[\cs{o}]{A}{B}}) & = & \cs{o} \\
    \pr(\ty{\typarr[\cs{o}]{A}{B}}) & = & \cs{o}
  \end{array}
  \qquad
  \begin{array}{lclclcl}
    \pr(\ty{\tynil[\cs{o}]})        & = & \cs{o} \\
    \pr(\ty{\tytop[\cs{o}]})        & = & \cs{o}
  \end{array}
  \qquad
  \begin{array}{lclclcl}
    \pr(\ty{\typlus[\cs{o}]{A}{B}}) & = & \cs{o} \\
    \pr(\ty{\tywith[\cs{o}]{A}{B}}) & = & \cs{o} 
  \end{array}
\]
\[
  \begin{array}{l}
    \minpr(\ty{\emptyenv})          = \cs{\ptop}
    \\
    \minpr(\ty{\Gamma},\tmty{x}{A}) = \minpr(\ty{\Gamma})\sqcap\minpr(\ty{A})
  \end{array}
\]

@@

\subsubsection*{Translation}
We illustrate the relation between PCP and PGV by giving a translation from PCP to PGV. The translation on types is defined as follows:
\[
  \begin{array}{lcl}
    \ty{\cpgvT{\pcp{\tytens[\cs{o}]{A}{B}}}}
    & = & \pgv{\ty{\tysend[\cs{o}]{\co{\cpgvT{A}}}{\cpgvT{B}}}}
    \\
    \ty{\cpgvT{\pcp{\typlus[\cs{o}]{A}{B}}}}
    & = & \pgv{\ty{\tyselect[\cs{o}]{\cpgvT{A}}{\cpgvT{B}}}}
  \end{array}
  \;
  \begin{array}{lcl}
    \ty{\cpgvT{\pcp{\tyone[\cs{o}]}}}
    & = & \ty{\pgv{\tyends[\cs{o}]}}
    \\
    \ty{\cpgvT{\pcp{\tynil[\cs{o}]}}}
    & = & \pgv{\ty{\tyselectemp[\cs{o}]}}
  \end{array}
  \;
  \begin{array}{lcl}
    \ty{\cpgvT{\pcp{\typarr[\cs{o}]{A}{B}}}}
    & = & \pgv{\ty{\tyrecv[\cs{o}]{\cpgvT{A}}{\cpgvT{B}}}}
    \\
    \ty{\cpgvT{\pcp{\tywith[\cs{o}]{A}{B}}}}
    & = & \pgv{\ty{\tyoffer[\cs{o}]{\cpgvT{A}}{\cpgvT{B}}}}
  \end{array}
  \;
  \begin{array}{lcl}
    \ty{\cpgvT{\pcp{\tybot[\cs{o}]}}}
    & = & \ty{\pgv{\tyendr[\cs{o}]}}
    \\
    \ty{\cpgvT{\pcp{\tytop[\cs{o}]}}}
    & = & \pgv{\ty{\tyofferemp[\cs{o}]}}
  \end{array}
\]
There are two separate translations on processes. The first, $\tm{\cpgvC{\cdot}}$, translates processes to \emph{configurations}:
\begin{align*}
  &\pcp{\tm{\cpgvC{\res{x}{y}{P}}}}
  &&= \pgv{\tm{\res{x}{y}{\cpgvC{P}}}}
  \\
  &\pcp{\tm{\cpgvC{\ppar{P}{Q}}}}
  &&= \pgv{\tm{\ppar{\cpgvC{P}}{\cpgvC{Q}}}}
  \\
  &\pcp{\tm{\cpgvC{\send{x}{y}{P}}}}
  &&= \pgv{\tm{\res{y}{z}{(\child\;\letbind{x}{\send\;\pair{z}{x}}{\cpgvM{P}})}}}
  \\
  &\pcp{\tm{\cpgvC{\inl{x}{P}}}}
  &&= \pgv{\tm{\res{y}{z}{(\child\;\letbind{x}{\andthen{\close\;(\send\;\pair{\inl{y}}{x})}{z}}{\cpgvM{P}})}}}
  \\
  &\pcp{\tm{\cpgvC{\inr{x}{P}}}}
  &&= \pgv{\tm{\res{y}{z}{(\child\;\letbind{x}{\andthen{\close\;(\send\;\pair{\inr{y}}{x})}{z}}{\cpgvM{P}})}}}
  \\
  &\pcp{\tm{\cpgvC{P}}}
  &&= \pgv{\tm{\child{\cpgvM{P}}}},\quad\text{if none of the above apply}
\end{align*}
The third, fourth, and fifth cases translate the $\nu$-binders in the translation of bound sending to configuration constructs, which is required for completeness of the operational correspondence.
It translates as much as possible of the process to the corresponding configuration constructs. Once it hits the first action, it switches to the second translation, $\tm{\cpgvM{\cdot}}$, which translates processes to \emph{terms}:
\begin{align*}
  &\pcp{\tm{\cpgvM{\link{x}{y}}}}
  &&= \pgv{\tm{\link\;{\pair{x}{y}}}} \\
  &\pcp{\tm{\cpgvM{\res{x}{y}{P}}}}
  &&= \pgv{\tm{\letpair{x}{y}{\new}{\cpgvM{P}}}} \\
  &\pcp{\tm{\cpgvM{\ppar{P}{Q}}}}
  &&= \pgv{\tm{\andthen{\spawn\;{(\lambda\unit.\cpgvM{P})}}{\cpgvM{Q}}}} \\
  &\pcp{\tm{\cpgvM{\halt}}}
  &&= \pgv{\tm{\unit}} \\
  &\pcp{\tm{\cpgvM{\close{x}{P}}}}
  &&= \pgv{\tm{\andthen{\close\;{x}}{\cpgvM{P}}}} \\
  &\pcp{\tm{\cpgvM{\wait{x}{P}}}}
  &&= \pgv{\tm{\andthen{\wait\;{x}}{\cpgvM{P}}}} \\
  &\pcp{\tm{\cpgvM{\send{x}{y}{P}}}}
  &&= \pgv{\tm{\letpair{y}{z}{\new}{\letbind{x}{\send\;{\pair{z}{x}}}{\cpgvM{P}}}}} \\
  &\pcp{\tm{\cpgvM{\recv{x}{y}{P}}}}
  &&= \pgv{\tm{\letpair{y}{x}{\recv\;{x}}{\cpgvM{P}}}} \\
  &\pcp{\tm{\cpgvM{\inl{x}{P}}}}
  &&= \pgv{\tm{\letbind{x}{\select{\labinl}\;{x}}{\cpgvM{P}}}} \\
  &\pcp{\tm{\cpgvM{\inr{x}{P}}}}
  &&= \pgv{\tm{\letbind{x}{\select{\labinr}\;{x}}{\cpgvM{P}}}} \\
  &\pcp{\tm{\cpgvM{\offer{x}{P}{Q}}}}
  &&= \pgv{\tm{\offer{x}{x}{\cpgvM{P}}{x}{\cpgvM{Q}}}} \\
  &\pcp{\tm{\cpgvM{\absurd{x}}}}
  &&= \pgv{\tm{\offeremp{x}}}
\end{align*}
Typing environments are translated pointwise, and sequents $\pcp{\seq{P}{\ty{\Gamma}}}$ are translated as $\pgv{\cseq[\child]{\ty{\cpgvT{\ty{\Gamma}}}}{\cpgvC{P}}}$.

The translations $\tm{\cpgvC{\cdot}}$ and $\tm{\cpgvM{\cdot}}$ preserve typing. The proofs are standard inductions. The details can be found in~\cref{prf:lem-pcp-to-pgv-terms-preservation,prf:lem-pcp-to-pgv-terms-preservation}:
\begin{compacttheorems}
  \begin{restatablelemma}{lempcptopgvtermspreservation}[Preservation, ${\tm{\cpgvM{\cdot}}}$]
    \label{lem:pcp-to-pgv-terms-preservation}
    If $\pcp{\seq{P}{\ty{\Gamma}}}$, then $\pgv{\tseq[\cs{p}]{\ty{\cpgvT{\Gamma}}}{\cpgvM{P}}{\tyunit}}$.
  \end{restatablelemma}
  \begin{restatabletheorem}{thmpcptopgvconfspreservation}[Preservation, ${\tm{\cpgvC{\cdot}}}$]
    \label{thm:pcp-to-pgv-confs-preservation}
    If $\pcp{\seq{P}{\ty{\Gamma}}}$, then $\pgv{\cseq[\child]{\ty{\cpgvT{\Gamma}}}{\cpgvC{P}}}$.
  \end{restatabletheorem}
\end{compacttheorems}

Our translation satisfies soundness and completeness of operational correspondence. We link ${\tm{\cpgvM{\cdot}}}$ and ${\tm{\cpgvC{\cdot}}}$ and show that $\tm{\cpgvM{P}}$ \emph{must} reduce to $\tm{\cpgvC{P}}$, \ie $\tm{\cpgvC{\cdot}}$ is equivalent to translating with $\tm{\cpgvM{\cdot}}$ and performing several reduction steps. We use this fact to prove the results below. The details are in~\cref{prf:lem-pcp-to-pgv-cpgvM-to-cpgvC,prf:thm-pcp-to-pgv-operational-correspondence-completeness,prf:thm-pcp-to-pgv-operational-correspondence-soundness}:
  \begin{restatablelemma}{lempcptopgvcpgvMtocpgvC}
    \label{lem:pcp-to-pgv-cpgvM-to-cpgvC}
    For any $\pcp{\tm{P}}$, either:
    \begin{itemize}
    \item $\pgv{\tm{\child\;\cpgvM{P}}=\tm{\cpgvC{P}}}$; or
    \item   $\pgv{\tm{\child\;\cpgvM{P}}\cred^+\tm{\cpgvC{P}}}$, and for any $\pgv{\tm{\conf{C}}}$, if $\pgv{\tm{\child\;\cpgvM{P}}\cred\tm{\conf{C}}}$, then $\pgv{\tm{\conf{C}}\cred^\star\tm{\cpgvC{P}}}$.
    \end{itemize}
  \end{restatablelemma}
  \begin{restatabletheorem}{thmpcptopgvoperationalcorrespondencesoundness}%
    [Operational Correspondence, Soundness, ${\tm{\cpgvC{\cdot}}}$]
    \label{thm:pcp-to-pgv-operational-correspondence-soundness}
    \hfill\\%newline before theorem statement
    If $\pcp{\seq{P}{\ty{\Gamma}}}$ and $\pgv{\tm{\cpgvC{P}}\cred\tm{\conf{C}}}$, there exists a $\tm{Q}$ such that $\pcp{\tm{P}\red^+\tm{Q}}$ and $\pgv{\tm{\conf{C}}\cred^\star\tm{\cpgvC{Q}}}$
  \end{restatabletheorem}
  % \begin{proof}
  %   By induction on the derivation of $\pgv{\tm{\cpgvC{P}}\cred\tm{\conf{C}}}$.\simon{Surprising that you can get it by the derivation of the reduction relation---normally, 'soundness' would be proved by shunting into a canonical form and then proceeding by induction the structure of the term / induction on typing derivations.}
  %   Details in \cref{prf:thm-pcp-to-pgv-operational-correspondence-soundness}.
  % \end{proof}
\begin{restatabletheorem}{thmpcptopgvoperationalcorrespondencecompleteness}%
  [Operational Correspondence, Completeness, ${\tm{\cpgvC{\cdot}}}$]
  \label{thm:pcp-to-pgv-operational-correspondence-completeness}
  \hfill\\%newline before theorem statement
  If $\pcp{\seq{P}{\ty{\Gamma}}}$ and $\pcp{\tm{P}\red\tm{Q}}$,
  then $\pgv{\tm{\cpgvC{P}}\cred^+\tm{\cpgvC{Q}}}$.
\end{restatabletheorem}
% \begin{proof}
%   By induction on the derivation of $\pcp{\tm{P}\red\tm{Q}}$. We apply \cref{lem:pcp-to-pgv-cpgvM-to-cpgvC} for the cases in which the translation switches from $\tm{\cpgvC{\cdot}}$ to $\tm{\cpgvM{\cdot}}$, \ie under actions. We apply \cref{lem:pcp-to-pgv-confs-operational-correspondence-equiv} for \LabTirName{E-LiftSC}. Details in \cref{prf:thm-pcp-to-pgv-operational-correspondence-completeness}.
% \end{proof}
\end{document}

>>>>

\subsubsection*{Priorities}
The function $\pr(\cdot)$ returns smallest priority of a type. As with PGV, the type system guarantees that the top-most connective always holds the smallest priority.  The function $\minpr(\cdot)$ returns the \emph{minimum} priority of all types a typing context, or $\cs{\ptop}$ if the context is empty:
\[
  \usingnamespace{pcp}
  \setlength{\arraycolsep}{1pt}
  \begin{array}{lclclcl}
    \pr(\ty{\tyone[\cs{o}]})        & = & \cs{o} \\
    \pr(\ty{\tybot[\cs{o}]})        & = & \cs{o}
  \end{array}
  \qquad
  \begin{array}{lclclcl}
    \pr(\ty{\tytens[\cs{o}]{A}{B}}) & = & \cs{o} \\
    \pr(\ty{\typarr[\cs{o}]{A}{B}}) & = & \cs{o}
  \end{array}
  \qquad
  \begin{array}{lclclcl}
    \pr(\ty{\tynil[\cs{o}]})        & = & \cs{o} \\
    \pr(\ty{\tytop[\cs{o}]})        & = & \cs{o}
  \end{array}
  \qquad
  \begin{array}{lclclcl}
    \pr(\ty{\typlus[\cs{o}]{A}{B}}) & = & \cs{o} \\
    \pr(\ty{\tywith[\cs{o}]{A}{B}}) & = & \cs{o} 
  \end{array}
\]
\[
  \minpr(\ty{\emptyenv})          = \cs{\ptop}
  \quad
  \minpr(\ty{\Gamma},\tmty{x}{A}) = \minpr(\ty{\Gamma})\sqcap\minpr(\ty{A})
\]

@@

\subsubsection*{Translation}
We illustrate the relation between PCP and PGV by giving a translation from PCP to PGV. The translation on types is defined as follows:
\[
  \begin{array}{lcl}
    \ty{\cpgvT{\pcp{\tytens[\cs{o}]{A}{B}}}}
    & = & \pgv{\ty{\tysend[\cs{o}]{\co{\cpgvT{A}}}{\cpgvT{B}}}}
    \\
    \ty{\cpgvT{\pcp{\typlus[\cs{o}]{A}{B}}}}
    & = & \pgv{\ty{\tyselect[\cs{o}]{\cpgvT{A}}{\cpgvT{B}}}}
  \end{array}
  \;
  \begin{array}{lcl}
    \ty{\cpgvT{\pcp{\tyone[\cs{o}]}}}
    & = & \ty{\pgv{\tyends[\cs{o}]}}
    \\
    \ty{\cpgvT{\pcp{\tynil[\cs{o}]}}}
    & = & \pgv{\ty{\tyselectemp[\cs{o}]}}
  \end{array}
  \;
  \begin{array}{lcl}
    \ty{\cpgvT{\pcp{\typarr[\cs{o}]{A}{B}}}}
    & = & \pgv{\ty{\tyrecv[\cs{o}]{\cpgvT{A}}{\cpgvT{B}}}}
    \\
    \ty{\cpgvT{\pcp{\tywith[\cs{o}]{A}{B}}}}
    & = & \pgv{\ty{\tyoffer[\cs{o}]{\cpgvT{A}}{\cpgvT{B}}}}
  \end{array}
  \;
  \begin{array}{lcl}
    \ty{\cpgvT{\pcp{\tybot[\cs{o}]}}}
    & = & \ty{\pgv{\tyendr[\cs{o}]}}
    \\
    \ty{\cpgvT{\pcp{\tytop[\cs{o}]}}}
    & = & \pgv{\ty{\tyofferemp[\cs{o}]}}
  \end{array}
\]

There are two separate translations on processes. The main translation, $\tm{\cpgvM{\cdot}}$, translates processes to \emph{terms}:
\begin{align*}
  &\pcp{\tm{\cpgvM{\link{x}{y}}}}
  &&= \pgv{\tm{\link\;{\pair{x}{y}}}} \\
  &\pcp{\tm{\cpgvM{\res{x}{y}{P}}}}
  &&= \pgv{\tm{\letpair{x}{y}{\new}{\cpgvM{P}}}} \\
  &\pcp{\tm{\cpgvM{\ppar{P}{Q}}}}
  &&= \pgv{\tm{\andthen{\spawn\;{(\lambda\unit.\cpgvM{P})}}{\cpgvM{Q}}}} \\
  &\pcp{\tm{\cpgvM{\halt}}}
  &&= \pgv{\tm{\unit}} \\
  &\pcp{\tm{\cpgvM{\close{x}{P}}}}
  &&= \pgv{\tm{\andthen{\close\;{x}}{\cpgvM{P}}}} \\
  &\pcp{\tm{\cpgvM{\wait{x}{P}}}}
  &&= \pgv{\tm{\andthen{\wait\;{x}}{\cpgvM{P}}}} \\
  &\pcp{\tm{\cpgvM{\send{x}{y}{P}}}}
  &&= \pgv{\tm{\letpair{y}{z}{\new}{\letbind{x}{\send\;{\pair{z}{x}}}{\cpgvM{P}}}}} \\
  &\pcp{\tm{\cpgvM{\recv{x}{y}{P}}}}
  &&= \pgv{\tm{\letpair{y}{x}{\recv\;{x}}{\cpgvM{P}}}} \\
  &\pcp{\tm{\cpgvM{\inl{x}{P}}}}
  &&= \pgv{\tm{\letbind{x}{\select{\labinl}\;{x}}{\cpgvM{P}}}} \\
  &\pcp{\tm{\cpgvM{\inr{x}{P}}}}
  &&= \pgv{\tm{\letbind{x}{\select{\labinr}\;{x}}{\cpgvM{P}}}} \\
  &\pcp{\tm{\cpgvM{\offer{x}{P}{Q}}}}
  &&= \pgv{\tm{\offer{x}{x}{\cpgvM{P}}{x}{\cpgvM{Q}}}} \\
  &\pcp{\tm{\cpgvM{\absurd{x}}}}
  &&= \pgv{\tm{\offeremp{x}}}
\end{align*}

Unfortunately, the operational correspondence along $\tm{\cpgvM{\cdot}}$ is incomplete, as it translates $\nu$-binders and parallel compositions to $\pgv{\tm{\new}}$ and $\pgv{\tm{\spawn}}$, which reduce back to their equivalent configuration constructs using \LabTirName{E-New} and \LabTirName{E-Spawn}. The same goes for $\nu$-binders which are inserted as a result of translating bound send to unbound send. For instance, the process $\pcp{\tm{\send{x}{y}{P}}}$ is blocked, but its translation uses $\pgv{\tm{\new}}$ and can reduce. To address this issue, we use a second translation, $\tm{\cpgvC{\cdot}}$, which is equivalent to $\tm{\cpgvM{\cdot}}$ followed by reduction using \LabTirName{E-New} and \LabTirName{E-Spawn}:
\begin{align*}
  &\pcp{\tm{\cpgvC{\res{x}{y}{P}}}}
  &&= \pgv{\tm{\res{x}{y}{\cpgvC{P}}}}
  \\
  &\pcp{\tm{\cpgvC{\ppar{P}{Q}}}}
  &&= \pgv{\tm{\ppar{\cpgvC{P}}{\cpgvC{Q}}}}
  \\
  &\pcp{\tm{\cpgvC{\send{x}{y}{P}}}}
  &&= \pgv{\tm{\res{y}{z}{(\child\;\letbind{x}{\send\;\pair{z}{x}}{\cpgvM{P}})}}}
  \\
  &\pcp{\tm{\cpgvC{\inl{x}{P}}}}
  &&= \pgv{\tm{\res{y}{z}{(\child\;\letbind{x}{\andthen{\close\;(\send\;\pair{\inl{y}}{x})}{z}}{\cpgvM{P}})}}}
  \\
  &\pcp{\tm{\cpgvC{\inr{x}{P}}}}
  &&= \pgv{\tm{\res{y}{z}{(\child\;\letbind{x}{\andthen{\close\;(\send\;\pair{\inr{y}}{x})}{z}}{\cpgvM{P}})}}}
  \\
  &\pcp{\tm{\cpgvC{P}}}
  &&= \pgv{\tm{\child{\cpgvM{P}}}},\quad\text{if none of the above apply}
\end{align*}

Typing environments are translated pointwise, and sequents $\pcp{\seq{P}{\ty{\Gamma}}}$ are translated as $\pgv{\cseq[\child]{\ty{\cpgvT{\ty{\Gamma}}}}{\cpgvC{P}}}$.
The translations $\tm{\cpgvM{\cdot}}$ and $\tm{\cpgvC{\cdot}}$ preserve typing, and the latter induces a sound and complete operational correspondence. The proofs are standard inductions. The details can be found in~\cref{prf:lem-pcp-to-pgv-terms-preservation,prf:lem-pcp-to-pgv-terms-preservation,prf:lem-pcp-to-pgv-cpgvM-to-cpgvC,prf:thm-pcp-to-pgv-operational-correspondence-soundness,prf:thm-pcp-to-pgv-operational-correspondence-completeness}.
\begin{compacttheorems}
  \begin{restatablelemma}{lempcptopgvtermspreservation}[Preservation, ${\tm{\cpgvM{\cdot}}}$]
    \label{lem:pcp-to-pgv-terms-preservation}
    If $\pcp{\seq{P}{\ty{\Gamma}}}$, then $\pgv{\tseq[\cs{p}]{\ty{\cpgvT{\Gamma}}}{\cpgvM{P}}{\tyunit}}$.
  \end{restatablelemma}
  \begin{restatabletheorem}{thmpcptopgvconfspreservation}[Preservation, ${\tm{\cpgvC{\cdot}}}$]
    \label{thm:pcp-to-pgv-confs-preservation}
    If $\pcp{\seq{P}{\ty{\Gamma}}}$, then $\pgv{\cseq[\child]{\ty{\cpgvT{\Gamma}}}{\cpgvC{P}}}$.
  \end{restatabletheorem}
  \begin{restatablelemma}{lempcptopgvcpgvMtocpgvC}
    \label{lem:pcp-to-pgv-cpgvM-to-cpgvC}
    For any $\pcp{\tm{P}}$, either:
    \begin{itemize}
    \item $\pgv{\tm{\child\;\cpgvM{P}}=\tm{\cpgvC{P}}}$; or
    \item   $\pgv{\tm{\child\;\cpgvM{P}}\cred^+\tm{\cpgvC{P}}}$, and for any $\pgv{\tm{\conf{C}}}$, if $\pgv{\tm{\child\;\cpgvM{P}}\cred\tm{\conf{C}}}$, then $\pgv{\tm{\conf{C}}\cred^\star\tm{\cpgvC{P}}}$.
    \end{itemize}
  \end{restatablelemma}
  \begin{restatabletheorem}{thmpcptopgvoperationalcorrespondencesoundness}%
    [Operational Correspondence, Soundness, ${\tm{\cpgvC{\cdot}}}$]
    \label{thm:pcp-to-pgv-operational-correspondence-soundness}
    \hfill\\%newline before theorem statement
    If $\pcp{\seq{P}{\ty{\Gamma}}}$ and $\pgv{\tm{\cpgvC{P}}\cred\tm{\conf{C}}}$, there exists a $\tm{Q}$ such that $\pcp{\tm{P}\red^+\tm{Q}}$ and $\pgv{\tm{\conf{C}}\cred^\star\tm{\cpgvC{Q}}}$
  \end{restatabletheorem}
  \begin{restatabletheorem}{thmpcptopgvoperationalcorrespondencecompleteness}%
    [Operational Correspondence, Completeness, ${\tm{\cpgvC{\cdot}}}$]
    \label{thm:pcp-to-pgv-operational-correspondence-completeness}
    \hfill\\%newline before theorem statement
    If $\pcp{\seq{P}{\ty{\Gamma}}}$ and $\pcp{\tm{P}\red\tm{Q}}$,
    then $\pgv{\tm{\cpgvC{P}}\cred^+\tm{\cpgvC{Q}}}$.
  \end{restatabletheorem}
\end{compacttheorems}
\end{document}
